Learning Auditory Similarities Between Instrumental Playing Techniques

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
comment on the use of the word "opportunistic"

What the higher levels of the auditory cortex does remains largely unknown, but we can assume that the degree of freedom of the underlying model is very large contrary to the early stages.  We will assume in this paper that this second step is rather opportunistic. From the large set of features it receives, this second stage aims at multiplexing in some way the ones that are the most relevant for the task at hand. Related work includes the use of the auditory model proposed by Shamma for studying musical timbre \cite{patil2012music}.

@@

\vl{Too much passive form in this subsection. @writing}

>>>>

What the higher levels of the auditory cortex does remains largely unknown, but we can assume that the degree of freedom of the underlying model is very large, unlike at the early stages.  We will assume in this paper that this second step is rather opportunistic. From the large set of features it receives, this second stage aims at multiplexing in some way the ones that are the most relevant for the task at hand. Related work includes the use of the auditory model proposed by Shamma for studying musical timbre \cite{patil2012music}.

\vl{The paragraph above is extremely vague. I don't think that "opportunistic" is the word we're looking for here. @writing}

@@

\vl{Too much passive form in this subsection. This last paragraph ("a renowned French school of music") is un-academic. @writing}
